Exploratory Plots

### 2020-09-10 exploratory/2020/sub3_fit_subsets.Rmd
Use boxplot & jitter geoms

```{r fit_ref_frac}
sensspec_fit %>%
  group_by(dataset, method) %>%
  ggplot(aes(x = ref_frac, y = mcc, color = dataset)) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(method ~ ref_weight)
```

@@

## Runtime
```{r}
benchmarks_fit <-
  read_tsv(here('subworkflows/2_fit_reference_db/results/benchmarks.tsv'))
benchmarks_fit %>% 
    group_by(dataset, method) %>%
    ggplot(aes(x = method, y = s, color = dataset)) +
    geom_boxplot() +
    scale_color_manual(values = dataset_colors) +
    #facet_wrap("ref_weight") +
    ylim(0,2100) +
    labs(y = 'seconds') +
    theme(axis.title.x = element_blank())
```

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  ggplot(aes(x=ref_weight, y=fraction_mapped, color=dataset)) +
  geom_boxplot(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("dataset", nrow = 1) + 
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit")
```

>>>>

```{r fit_ref_frac_open}
sensspec_fit %>%
  filter(method == 'open') %>% 
  group_by(dataset, ref_weight) %>%
  ggplot(aes(x = as.factor(ref_frac), y = mcc, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(dataset ~ ref_weight) +
  labs(title='Open-reference OptiFit Performance',
       x='reference fraction')
```

```{r fit_ref_frac_closed}
sensspec_fit %>%
  filter(method == 'closed') %>% 
  group_by(dataset, ref_weight) %>%
  ggplot(aes(x = as.factor(ref_frac), y = mcc, color = dataset)) +
  geom_boxplot() +
  scale_color_manual(values = dataset_colors) +
  ylim(0.5, 1) +
  facet_grid(dataset ~ ref_weight) +
  labs(title='Closed-reference OptiFit Performance',
       x='reference fraction')
```

@@

## Runtime
```{r runtime_ref_size}
runtime <- full_join(
  read_tsv(here('subworkflows/3_fit_sample_subset/results/benchmarks.tsv')),
  read_tsv(here('subworkflows/3_fit_sample_subset/results/input_sizes.tsv'))
  )
runtime %>% ggplot(aes(x=num_ref_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  labs(title = 'Runtime over reference size',
       x = '# sequences in reference',
       y = 'seconds')
```

```{r runtime_sample_size}
runtime %>% ggplot(aes(x=num_sample_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  labs(title = 'Runtime over sample size',
       x = '# sequences in sample',
       y = 'seconds')
```

## Fraction of sequences that map to the reference
```{r fraction_reads_mapped}
fractions <- read_tsv(here('subworkflows/3_fit_sample_subset/results/fraction_reads_mapped.tsv'))
fractions %>% 
  group_by(dataset, ref_weight, ref_frac) %>% 
  ggplot(aes(x=ref_frac, y=fraction_mapped, color=dataset)) +
  geom_jitter(alpha = 0.5, width = 0.01, size=1) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref_weight") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit",
       x='reference fraction',
       y='fraction mapped')
```
